Exploration

### 2018-03-12 exploration.Rmd
corrected N>0 instead of N>1

IPM.fit.sum <- lam.df %>% 
  summarise(mnLamDiff=mean(lambda.f-lambda),
            mdLamDiff=median(lambda.f-lambda),
            sdLamDiff=sd(lambda.f-lambda),
            pctLamCorr=mean((lambda>1 & lambda.f>1) | (lambda<1 & lambda.f<1)),
            mnNDiff=mean(N.S.f-N.S),
            mdNDiff=median(N.S.f-N.S),
            sdNDiff=sd(N.S.f-N.S),
            pctNCorr=mean((N.S>1 & N.S.f>1) | (N.S<1 & N.S.f<1)),
            mnSurvDiff=mean(Surv.S.f-Surv.S),
            mdSurvDiff=median(Surv.S.f-Surv.S),
            sdSurvDiff=sd(Surv.S.f-Surv.S),
            pctSurvCorr=mean((Surv.S>1 & Surv.S.f>1) | (Surv.S<1 & Surv.S.f<1)),
            mnRcrDiff=mean(Rcr.S.f-Rcr.S),
            mdRcrDiff=median(Rcr.S.f-Rcr.S),
            sdRcrDiff=sd(Rcr.S.f-Rcr.S),
            pctRcrCorr=mean((Rcr.S>1 & Rcr.S.f>1) | (Rcr.S<1 & Rcr.S.f<1)))
```

>>>>

IPM.fit.sum <- lam.df %>% 
  summarise(mnLamDiff=mean(lambda.f-lambda),
            mdLamDiff=median(lambda.f-lambda),
            sdLamDiff=sd(lambda.f-lambda),
            pctLamCorr=mean((lambda>1 & lambda.f>1) | (lambda<1 & lambda.f<1)),
            mnNDiff=mean(N.S.f-N.S),
            mdNDiff=median(N.S.f-N.S),
            sdNDiff=sd(N.S.f-N.S),
            pctNCorr=mean((N.S>0 & N.S.f>0) | (N.S<0 & N.S.f<0)),
            mnSurvDiff=mean(Surv.S.f-Surv.S),
            mdSurvDiff=median(Surv.S.f-Surv.S),
            sdSurvDiff=sd(Surv.S.f-Surv.S),
            pctSurvCorr=mean((Surv.S>0 & Surv.S.f>0) | (Surv.S<0 & Surv.S.f<0)),
            mnRcrDiff=mean(Rcr.S.f-Rcr.S),
            mdRcrDiff=median(Rcr.S.f-Rcr.S),
            sdRcrDiff=sd(Rcr.S.f-Rcr.S),
            pctRcrCorr=mean((Rcr.S>0 & Rcr.S.f>0) | (Rcr.S<0 & Rcr.S.f<0)))
```
